\textsf{Are large language models superhuman chemists?}

### 2024-03-21 src/tex/appendix.tex
typesetting

\begin{figure}[htb]
    \centering
    \includegraphics{figures/parallel_coordinates_human_aligned.pdf}
    \caption{\textbf{Performance of the models on the different topics of the \enquote{tiny} subset.} The parallel coordinates plot shows the performance of the models on the different topics of the \enquote{tiny} subset. The performance is measured as the fraction of questions that were answered completely correctly by the models. }
    \label{fig:parallel_coordinates_human_aligned}
    \script{make_parallel_coordinates_plot.py}
\end{figure}

@@

We also recorded the time humans took to answer the questions. This time is the time from the question being displayed to the human to the human submitting the answer.
Interestingly, we found no significant correlation between the experience of the human scorers and the performance on the questions (\Cref{fig:human_timing}, Spearman's \(\rho \approx \variable{output/spearman_experience_score.txt}\), \(p \approx \variable{output/spearman_experience_score_p.txt}\)).

@@

Additionally, we prompted users to provide additional information about their experience in chemistry. 
While we recorded very fine-grained information, e.g., including their specialization, we focussed our analysis on the number of years since the first university-level chemistry course.
\Cref{fig:experience_vs_correctness} shows that the experience of the human scorers was not significantly correlated with the correctness of their answers (\Cref{fig:experience_vs_correctness}, Spearman's \(\rho \approx \variable{output/spearman_experience_score.txt}\), \(p \approx \variable{output/spearman_experience_score_p.txt}\)).

@@

Since it is important to understand if models can provide an indication of whether their answer might likely be incorrect, we prompted some of our top performing \glspl{llm} to return the confidence in providing a correct answer on an ordinal scale.

\Cref{fig:confidence_score_distributions} plots the distribution of those scores.

>>>>

\begin{figure}[htb]
    \centering
    \includegraphics{figures/parallel_coordinates_tiny.pdf}
    \caption{\textbf{Performance of the models on the different topics of the \enquote{tiny} subset.} The parallel coordinates plot shows the performance of the models on the different topics of the \enquote{tiny} subset. The performance is measured as the fraction of questions that were answered completely correctly by the models. }
    \label{fig:parallel_coordinates_tiny}
    \script{make_parallel_coordinates_plot.py}
\end{figure}

@@

We also recorded the time humans took to answer the questions. This time is the time from the question being displayed to the human to the human submitting the answer.
Interestingly, we found no significant correlation between the experience of the human scorers and the performance on the questions (\Cref{fig:human_timing}, Spearman's \(\rho \approx \variable{output/spearman_experience_score.txt}\), and \(p \approx \variable{output/spearman_experience_score_p.txt}\)).

@@

Additionally, we prompted users to provide additional information about their experience in chemistry. 
While we recorded very fine-grained information, e.g., including their specialization, we focussed our analysis on the number of years since the first university-level chemistry course.
\Cref{fig:experience_vs_correctness} shows that the experience of the human scorers was not significantly correlated with the correctness of their answers (\Cref{fig:experience_vs_correctness}, Spearman's \(\rho \approx \variable{output/spearman_experience_score.txt}\), and \(p \approx \variable{output/spearman_experience_score_p.txt}\)).

@@

Since it is important to understand if models can provide an indication of whether their answer might likely be incorrect, we prompted some of our top performing \glspl{llm} to return the confidence in providing a correct answer on an ordinal scale. 
This is similar to the verbalized confidence scores reported by \textcite{xiong2023llms}.
\Cref{fig:confidence_score_distributions} plots the distribution of those scores.
We find that the models show different distributions of confidence scores, which for some are skewed to the extremes.
